Cochain level May-Steenrod operations

### 2021-06-30 main.tex
Improve abstract

\begin{abstract}
	Steenrod defined in 1947 the Steenrod squares on the mod 2 cohomology of spaces using explicit cochain formulae for the cup-$i$ products; a family of coherent homotopies derived from the broken symmetry of Alexander-Whitney's chain approximation to the diagonal. Later, following a viewpoint developed by Adem, Steenrod defined his homonymous operations for all primes using the homology of symmetric groups. This approach enhanced the conceptual understanding of the operations and allowed for many advances but lacked the concreteness of their definition at~$2$. In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- having a definition of Steenrod operations that can be effectively computed in specific examples has become a key issue. This article provides such definition, at all primes, using the operadic viewpoint of May for well known $E_\infty$-algebras including the cochains of spaces expressed via simplicial or cubical cell structures.
\end{abstract}

>>>>

\begin{abstract}
	Steenrod defined in 1947 the Steenrod squares on the mod 2 cohomology of spaces using explicit cochain formulae for the cup-$i$ products; a family of coherent homotopies derived from the broken symmetry of Alexander-Whitney's chain approximation to the diagonal. He later defined his homonymous operations for all primes using the homology of symmetric groups. This approach enhanced the conceptual understanding of the operations and allowed for many advances, but lacked the concreteness of their definition at the even prime. In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- having a definition of Steenrod operations that can be effectively computed in specific examples has become a key issue. This article provides such definition at all primes using the operadic viewpoint of May for certain well known $E_\infty$-algebras, including the cochains of spaces expressed via simplicial or cubical cell structures, for which we also describe multioperations generalizing the cup-$i$ products of Steenrod.
\end{abstract}
